Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-07-04 WSSSPE2_report/WSSSPE2_review.tex
Section 7: Line breaks.
Section 7.1.1: minor changes.

Finally, after agreeing that these complementary training models were needed,
the group discussed sustainability of training, and how the leading groups in
this space are teaching only a small fraction of the community that needs and
wants training. Most graduate programs in the sciences do not currently
incorporate these approaches in their graduate curricula, although there are an
increasing number of quantitatively oriented courses around analysis and
modeling. These still, however, generally omit engineering practices such as
version control, unit and regression testing, and software modularity and
abstraction, often because the instructors themselves in the domain sciences are
not familiar with these techniques. Thus, students who are being trained in
these approaches are doing so through short 2--3 day training workshops such as
Software and Data Carpentry, rather than through semester-long graduate
education courses at their University, which tend to focus on statistical and
modeling techniques. Hybrid programs like the three week Open Science for
Synthesis (OSS) training that combine the three (science, quantitative
techniques, and software engineering) into an holistic course serve part of the
need but reach only a few researchers at this time. Thus, the group concluded
that significant strides needed to be made in coordinating these trainings so
that they are complementary, on increasing their size and scope, and on better
integrating them directly into graduate education programs.

>>>>

Finally, after agreeing that these complementary training models were needed,
the group discussed sustainability of training, and how the leading groups in
this space are teaching only a small fraction of the community that needs and
wants training. Most graduate programs in the sciences do not currently
incorporate these approaches in their graduate curricula, although there is an
increasing number of quantitatively oriented courses around analysis and
modeling. These still, however, generally omit engineering practices such as
version control, unit and regression testing, and software modularity and
abstraction, often because the instructors themselves in the domain sciences are
not familiar with these techniques. Thus, students who are being trained in
these approaches are doing so through short 2--3 day training workshops such as
Software and Data Carpentry, rather than through semester-long graduate
education courses at their universities, which tend to focus on statistical and
modeling techniques. Hybrid programs like the three-week Open Science for
Synthesis (OSS) training that combine the three (science, quantitative
techniques, and software engineering) into an holistic course serve part of the
need but reach only a few researchers at this time. Thus, the group concluded
that significant strides needed to be made in coordinating these trainings so
that they are complementary, on increasing their size and scope, and on better
integrating them directly into graduate education programs.
